\chapter{Project Proposal \\
\small{\textit{-- JGa, JGr, CS}}
\index{Project Proposal} 
\index{Chapter!Project Proposal}
\label{Chapter::ProjectProposal}}
\section{Project Description}

Our project is our senior design project, GreekConnect, which is intended to be a web app and accompanying app which allows fraternities, sororities, and their members to schedule and view events.  Our users include Stevens faculty as well as a significant student body, so for our app to be useful it needs to be easy to install and open on a computer as well as a phone by students who likely don’t want to do very much in order to get access to the app.  Some features which we will need to test include:

\begin{itemize}
\item Does the app work when multiple people try to make changes at once?
\item Do transfers of roles and permissions work as intended?
\item Do students and student leaders see messages intended for them?
\end{itemize}

We will also need a database, as our app plans on storing the information of many people’s schedules.  Considering the Stevens database only appears to be a convenient option on campus, we expect to need to look into alternatives like an Amazon Web Server.  We will try out a few different options to determine the minimum specifications necessary for our needs.

\section{Dev Ops Tool Specification}
Source control management will be done using Git and Github, which will allow us to focus on testing and deployment collaboratively.
Deployment will likely use Docker to containerize the app for various environments and Kubernetes to orchestrate and maintain the containers.
Our project will likely use a synchronized database such as Firebase, which is a document-based NoSQL database, so that it’s easier to program user data editing/collaboration. We will also explore SQL based options such as Supabase, PostgreSQL and Neon depending on our planned coding schedule.
Testing will likely use Jest or other Javascript testing frameworks (React Testing Library, Cypress) to test the front and back end of the application. 
